---
title: "ws_appendix"
format: pdf
editor: visual
---

## replicate the paper F. Li(2008).

```{r, include = FALSE, echo: false}
library(readr)
library(dplyr)
library(tidyr)
library(fixest)
library(stringr)
library(summarytools)
library(knitr)
library(ggplot2)
library(patchwork)
library(lubridate)
library(mice)
library(lfe)
library(stargazer)
library(DescTools)



final <- read_csv("final.csv")
final$filing_date <- as.Date(final$filing_date, format="%m/%d/%Y")
final$year <- year(final$filing_date)
final$profit_dummy = ifelse(final$Earnings >= 0, 1, 0)
```

#Table 1

##(A) Summary statistics;

```{r}
#| echo: false
final <- final %>% 
  group_by(cik) %>%
  arrange(cik, year) %>% 
  mutate(fog_diff = fog_index - lag(fog_index),
         length_diff = length - lag(length),
         bog_diff = bogindex - lag(bogindex),
         mda_fog_diff = mda_fog_index - lag(mda_fog_index),
         mda_length_diff = mda_length - lag(mda_length)) %>% 
  ungroup()

vars <- c("Earnings", "mtb", "mve", "at", 
          "fog_index", "fog_diff", "length", "length_diff", "bogindex", "bog_diff",
          "mda_fog_index", "mda_fog_diff", "mda_length", "mda_length_diff")

summary_df <- descr(final[vars], 
                    stats = c("mean", "med", "sd", "q1", "q3", "n.valid"),
                    transpose = TRUE) 

original_order <- c("Book value of assets (\\$MM)", "Bog(t) - Bog(t-1)","Bog", "Earnings", 
                    "Fog(t) - Fog(t-1)", "Fog", "Length", "Length(t) - length(t-1)",
                    "(Fog(t) - Fog(t-1))(MD&A)", "Fog(MD&A)", "Length(MD&A)", "(Length(t) - length(t-1))(MD&A)",
                    "Market-to-book", "Market value of equity (\\$MM)")
desired_order <- c("Earnings", "Market-to-book", "Market value of equity (\\$MM)", "Book value of assets (\\$MM)",
                   "Fog", "Fog(t) - Fog(t-1)", "Length", "Length(t) - length(t-1)","Bog","Bog(t) - Bog(t-1)",
                   "Fog(MD&A)", "(Fog(t) - Fog(t-1))(MD&A)", "Length(MD&A)", "(Length(t) - length(t-1))(MD&A)")
rownames(summary_df) <- original_order
name_mapping <- setNames(desired_order, original_order)
summary_df1 <- summary_df[name_mapping[rownames(summary_df)], ]
summary_df1 <- data.frame(summary_df1)
colnames(summary_df1) <- c("Mean", "Median", "Std. Dev", "25th", "75th","N")
summary_df1[1:5] <- lapply(summary_df1[1:5], function(x) sprintf("%.2f", x))
summary_df1[] <- lapply(summary_df1, as.character)
year_stats <- as.data.frame(t(data.frame(Year = c("-", "2019", "-", "2017", "2020", "18626")))) #2016-2021
colnames(year_stats) <- c("Mean", "Median", "Std. Dev", "25th", "75th","N")

combined_df <- bind_rows(year_stats, summary_df1)

kable(combined_df, format = "html", escape = FALSE)

```

#Fig. 1. ##(A) Median Fog and Length of the whole annual report by calendar year of the filing date.

```{r,warning=FALSE}
#| echo: false
med <- final %>%
  group_by(year) %>% 
  summarise(
    med_fog = median(fog_index, na.rm = TRUE),
    med_mdafog = median(mda_fog_index, na.rm = TRUE),
    med_length = median(length, na.rm = TRUE),
    med_mdalength = median(mda_length, na.rm = TRUE),
    med_bog = median(bogindex, na.rm = TRUE))

#The whole annual report
range_fog <- max(med$med_fog) - min(med$med_fog)
range_length <- max(med$med_length) - min(med$med_length)
scale_factor <- range_fog / range_length

adjusted_length <- (med$med_length - min(med$med_length)) * scale_factor + min(med$med_fog)
expanded_y_min <- min(med$med_fog, min(adjusted_length)) - 0.1 * range_fog
expanded_y_max <- max(med$med_fog, max(adjusted_length)) + 0.1 * range_fog

p1 <- ggplot(med, aes(x = year)) +
  geom_line(aes(y = med_fog, colour = "Fog"), size = 1) +
  geom_point(aes(y = med_fog, colour = "Fog"), shape = 15, fill = "#C39BD3",size = 2) +
  geom_line(aes(y = adjusted_length, colour = "Length"), size = 1) +
  geom_point(aes(y = adjusted_length, colour = "Length"), shape = 17, fill = "#FFD700",size = 2) +
  scale_y_continuous(
    name = "Fog",
    limits = c(expanded_y_min, expanded_y_max), 
    sec.axis = sec_axis(~(. - min(med$med_fog)) / scale_factor + min(med$med_length), name = "Length")) +
  scale_colour_manual(values = c("Fog" = "#C39BD3", "Length" = "#FFD700")) +
  labs(title = "Fig. 1A. The whole annual report") +
  theme_minimal() +
  theme(
    legend.position = "top",  
    legend.justification = "left")

p2 <- ggplot(med, aes(x = year)) +
  geom_line(aes(y = med_bog), size = 1, color = "blue") +
  geom_point(aes(y = med_bog),size = 2, color = "blue") +
  labs(title = "Fig. 1B. The whole annual report",
       x = "Year",  
       y = "Bog") +
  theme_minimal()

p1
p2

```

##(B) Median Fog and Length of the MD&A section by calendar year of the filing date.

```{r,warning=FALSE}
#| echo: false
#MD&A Section
range_fog <- max(med$med_mdafog) - min(med$med_mdafog)
range_length <- max(med$med_mdalength) - min(med$med_mdalength)
scale_factor <- range_fog / range_length
adjusted_length <- (med$med_mdalength - min(med$med_mdalength)) * scale_factor + min(med$med_mdafog)

expanded_y_min <- min(med$med_mdafog, adjusted_length) - 0.1 * range_fog
expanded_y_max <- max(med$med_mdafog, adjusted_length) + 0.1 * range_fog

ggplot(med, aes(x = year)) +
  geom_line(aes(y = med_mdafog, colour = "Fog"), size = 1) +
  geom_point(aes(y = med_mdafog, colour = "Fog"), shape = 15, fill = "#C39BD3",size = 2) +
  geom_line(aes(y = adjusted_length, colour = "Length"), size = 1) +
  geom_point(aes(y = adjusted_length, colour = "Length"), shape = 17, fill = "#FFD700",size = 2) +
  scale_y_continuous(
    name = "Fog",
    limits = c(expanded_y_min, expanded_y_max),
    sec.axis = sec_axis(~ (. - min(med$med_mdafog)) / scale_factor + min(med$med_mdalength), name = "Length")
  ) +
  scale_colour_manual(values = c("Fog" = "#C39BD3", "Length" = "#FFD700")) +
  labs(title = "Fig. 2.MD&A Section") +
  theme_minimal()+
  theme(
    legend.position = "top",  
    legend.justification = "left")


```

#Table 2

##(A) Summary statistics of the determinants of Fog and Length;

```{r}
#| echo: false
vars <- c("age", "si", "RET_VOL", "EARN_VOL", 
          "NBSEG", "NGSEG", "NITEMS", "SEO", "MA", "DLW")

summary_df <- descr(final[vars], 
                    stats = c("mean", "med", "sd", "q1", "q3", "n.valid"),
                    transpose = TRUE) 

original_order <- c("AGE", "DLW","EARN_VOL", "MA", "NBSEG", "NGSEG", "NITEMS", "RET_VOL", "SEO", "SI")
desired_order <- c("AGE", "SI", "RET_VOL","EARN_VOL", "NBSEG", "NGSEG","NITEMS", "SEO", "MA", "DLW")
rownames(summary_df) <- original_order
name_mapping <- setNames(desired_order, original_order)
summary_df1 <- summary_df[name_mapping[rownames(summary_df)], ]
summary_df1 <- data.frame(summary_df1)
colnames(summary_df1) <- c("Mean", "Median", "Std. Dev", "25th", "75th","N")
summary_df1[1:5] <- lapply(summary_df1[1:5], function(x) sprintf("%.2f", x))
summary_df1[] <- lapply(summary_df1, as.character)
summary_df1[c("SEO", "MA","DLW"), c("Median", "Std. Dev", "25th", "75th")] <- "-"
kable(summary_df1, format = "html")
```

##(B) Determinants of Fog;

```{r, include = FALSE,warning=FALSE}
#| echo: false
final$sic2 <- substr(final$sic, 1, 2)
final <- final %>%
  arrange(cik, year) %>%  
  group_by(cik) %>%
  mutate(
    Earnings_change = Earnings - lag(Earnings),  
    Earnings_change_d = ifelse(Earnings_change > 0, 1, 0),
    earn_t1 = lead(Earnings,1),
    earn_t2 = lead(Earnings,2)) %>%
  ungroup()

#Imputation
imp <- mice(final[c("mda_fog_diff","mda_length_diff","mda_fog_index","mda_length","fog_index",
                    "length","profit_dummy","Earnings","Earnings_change","Earnings_change_d","earn_t1","earn_t2",
                    "fog_diff","length_diff","bog_diff","bogindex","mve","mtb","size","NBSEG",
                    "NGSEG", "RET_VOL","EARN_VOL","si","age","NITEMS","SEO","MA","DLW","year","sic2")],
            method = c('','','','','' ,'','','','','','','','','','','','pmm', 'pmm', 'pmm', 'pmm', 'pmm', 'pmm',
                       'pmm','pmm','','','','','','',''), seed = 66)
final_imp <- complete(imp, 1) 
#winsorization 
final_imp$Earnings_change <- 
  Winsorize(final_imp$Earnings_change, quantile(final_imp$Earnings_change, probs=c(0.01, 0.99), na.rm = TRUE))
final_imp$Earnings_change_d <- 
  Winsorize(final_imp$Earnings_change_d, quantile(final_imp$Earnings_change_d, probs=c(0.01, 0.99), na.rm = TRUE))
final_imp$mda_fog_diff <- 
  Winsorize(final_imp$mda_fog_diff, quantile(final_imp$mda_fog_diff, probs=c(0.01, 0.99), na.rm = TRUE))
final_imp$mda_length_diff <- 
  Winsorize(final_imp$mda_length_diff, quantile(final_imp$mda_length_diff, probs=c(0.01, 0.99), na.rm = TRUE))
```

```{r,warning=FALSE}
#| echo: false
model1 <- felm(fog_index ~ size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model2 <- felm(mda_fog_index ~ size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
stargazer(
  model1, model2, 
  type = "text",
  out = "~/Desktop/t1.txt",
  title = "Regression Results of Fog",
  dep.var.labels = c("Fog of the whole annual report","Fog of the MD&A section"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

##(C) Determinants of Length

```{r,warning=FALSE}
#| echo: false
model3 <- felm(length ~ size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model4 <- felm(mda_length ~ size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
stargazer(
  model3, model4, 
  type = "text",
  out = "~/Desktop/t2.txt",
  title = "Regression Results of Length",
  dep.var.labels = c("Length of the whole annual report","Length of the MD&A section"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

```{r,warning=FALSE}
#| echo: false
model5 <- felm(bogindex ~ size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)

stargazer(
  model5, 
  type = "text",
  out = "~/Desktop/t3.txt",
  title = "Regression Results of Bog Index",
  dep.var.labels = c("Bog of the whole annual report"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes"),
    c("Industry dummies", "Yes"),
    c("Cluster", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

#Table 3 ##(A) Firm performance and annual report Fog and Length (level specification);

```{r,warning=FALSE}
#| echo: false
model6 <- felm(fog_index ~ Earnings + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model7 <- felm(fog_index ~ profit_dummy + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

model8 <- felm(length ~ Earnings + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model9 <- felm(length ~ profit_dummy + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW|year+ sic2|0|sic2,
                data = final_imp)

model10 <- felm(bogindex ~ Earnings + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)
model11 <- felm(bogindex ~ profit_dummy + size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

stargazer(
  model6, model7, model8, model9, model10, model11,
  type = "text",
  out = "~/Desktop/t4.txt",
  title = "Firm performance and annual report Fog and Length (level specification) in Whole annual report",
  dep.var.labels = c("Fog","Length","Bog"),
  keep = c("Earnings", "profit_dummy"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2","Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)

```

```{r,warning=FALSE}
#| echo: false
model12 <- felm(mda_fog_index~Earnings+size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model13 <- felm(mda_fog_index~profit_dummy+size + mtb+ age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

model14 <- felm(mda_length~Earnings+size + mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model15 <- felm(mda_length~profit_dummy+size + mtb+ age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

stargazer(
  model12, model13, model14, model15,
  type = "text",
  out = "~/Desktop/t5.txt",
  title = "Firm performance and annual report Fog and Length (level specification) in MD&A Section",
  dep.var.labels = c("Fog","Length"),
  keep = c("Earnings", "profit_dummy"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

##(B) Firm performance and annual report Fog and Length (change specification)

```{r,warning=FALSE}
#| echo: false
model16 <- felm(fog_diff~Earnings_change+size+mtb+ age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model17 <- felm(fog_diff~Earnings_change_d+size+mtb +age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

model18 <- felm(length_diff~Earnings_change+size+mtb+age+ si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model19 <- felm(length_diff ~Earnings_change_d+size+mtb+age+ si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

model20 <- felm(bog_diff~Earnings_change+size+mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model21 <- felm(bog_diff~Earnings_change_d+size+ mtb + age + si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

stargazer(
  model16, model17, model18, model19, model20, model21,
  type = "text",
  out = "~/Desktop/t6.txt",
  title = "Firm performance and annual report Fog and Length (change specification) in Whole annual report",
  dep.var.labels = c("ΔFog","ΔLength","ΔBog"),
  keep = c("Earnings", "profit_dummy"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2","Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

```{r,warning=FALSE}
#| echo: false
model22 <- felm(mda_fog_diff~Earnings_change+size+mtb+age+si+ RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model23 <- felm(mda_fog_diff~Earnings_change_d+size+mtb+age+si + RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

model24 <- felm(mda_length_diff~Earnings_change+size+mtb+age+si+RET_VOL+ EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA + DLW| year + sic2|0|sic2,
                data = final_imp)
model25 <- felm(mda_length_diff~Earnings_change_d+size+mtb+age+si+RET_VOL + EARN_VOL + NBSEG + NGSEG + NITEMS + SEO + MA +DLW|year+ sic2|0|sic2,
                data = final_imp)

stargazer(
  model22, model23, model24, model25,
  type = "text",
  out = "~/Desktop/t7.txt",
  title = "Firm performance and annual report Fog and Length (change specification) in MD&A Section",
  dep.var.labels = c("ΔFog","ΔLength"),
  keep = c("Earnings", "profit_dummy"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

#Table 4 ##(A) Earnings persistence and annual report Fog index (profit firm-years);

```{r,warning=FALSE}
#| echo: false
final_imp1 <- final_imp %>% filter(profit_dummy == 1)
model26 <- felm(earn_t1~Earnings+fog_index+Earnings*fog_index+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model27 <- felm(earn_t2~Earnings+fog_index+Earnings*fog_index+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

model28 <- felm(earn_t1~Earnings+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model29 <- felm(earn_t2~Earnings+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

stargazer(
  model26, model27, model28, model29,
  type = "text",
  out = "~/Desktop/t8.txt",
  title = "Earnings Persistence and Annual Report Fog Index (Profit Firm-Years)",
  keep = c("Earnings", "fog_index","mda_fog_index","Earnings:fog_index","Earnings:mda_fog_index"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)

```

##(B) earnings persistence and annual report Length (profit firmyears);

```{r,warning=FALSE}
#| echo: false
model30 <- felm(earn_t1~Earnings+length+Earnings*length+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model31 <- felm(earn_t2~Earnings+length+Earnings*length+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

model32 <- felm(earn_t1~Earnings+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model33 <- felm(earn_t2~Earnings+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

stargazer(
  model30, model31, model32, model33,
  type = "text",
  out = "~/Desktop/t9.txt",
  title = "Earnings Persistence and Annual Report Length(Profit Firm-Years)",
  keep = c("Earnings", "length","mda_length","Earnings:length","Earnings:mda_length"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)

```

##(C) earnings persistence and annual report Bog (profit firmyears);

```{r,warning=FALSE}
#| echo: false
model34 <- felm(earn_t1~Earnings+bogindex+Earnings*bogindex+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model35 <- felm(earn_t2~Earnings+bogindex+Earnings*bogindex+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

stargazer(
  model34, model35,
  type = "text",
  out = "~/Desktop/t10.txt",
  title = "Earnings Persistence and Annual Report Bog index(Profit Firm-Years)",
  keep = c("Earnings", "bogindex","Earnings:bogindex"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes"),
    c("Control variables", "Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

##(D) earnings persistence and annual report readability (profit firm-years)

```{r,warning=FALSE}
#| echo: false
model36 <- felm(earn_t1~Earnings+fog_index+Earnings*fog_index+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model37 <- felm(earn_t2~Earnings+fog_index+Earnings*fog_index+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model38 <- felm(earn_t1~Earnings+length+Earnings*length+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)
model39 <- felm(earn_t2~Earnings+length+Earnings*length+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp1)

stargazer(
  model36, model37,model38, model39,
  type = "text",
  out = "~/Desktop/t11.txt",
  title = "Earnings persistence and annual report readability(Profit Firm-Years)",
  keep = c("Earnings", "fog_index","length","Earnings*fog_index","Earnings*length","mda_fog_index","mda_length","Earnings*mda_fog_index","Earnings*mda_length"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes", "Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes", "Yes", "Yes"),
    c("Control variables", "Yes", "Yes", "Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

#Table 5 ##(A) Earnings persistence and annual report Fog index (loss firm-years);

```{r,warning=FALSE}
#| echo: false
final_imp0 <- final_imp %>% filter(profit_dummy == 0)
model40 <- felm(earn_t1~Earnings+fog_index+Earnings*fog_index+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)
model41 <- felm(earn_t2~Earnings+fog_index+Earnings*fog_index+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)

model42 <- felm(earn_t1~Earnings+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)
model43 <- felm(earn_t2~Earnings+mda_fog_index+Earnings*mda_fog_index
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)

stargazer(
  model40, model41, model42, model43,
  type = "text",
  out = "~/Desktop/t12.txt",
  title = "Earnings Persistence and Annual Report Fog Index (loss Firm-Years)",
  keep = c("Earnings", "fog_index","mda_fog_index","Earnings:fog_index","Earnings:mda_fog_index"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)
```

##(B) earnings persistence and annual report Length (loss firm-years)

```{r,warning=FALSE}
#| echo: false
model44 <- felm(earn_t1~Earnings+length+Earnings*length+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)
model45 <- felm(earn_t2~Earnings+length+Earnings*length+size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)

model46 <- felm(earn_t1~Earnings+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)
model47 <- felm(earn_t2~Earnings+mda_length+Earnings*mda_length
                +size+mtb+age+si+RET_VOL+EARN_VOL+NBSEG+NGSEG+NITEMS+SEO+MA+DLW|year+sic2|0|sic2,
                data = final_imp0)

stargazer(
  model44, model45, model46, model47,
  type = "text",
  out = "~/Desktop/t13.txt",
  title = "Earnings Persistence and Annual Report Length(loss Firm-Years)",
  keep = c("Earnings", "length","mda_length","Earnings:length","Earnings:mda_length"),
  report = "vc*t",
  add.lines = list(
    c("Year dummies", "Yes", "Yes","Yes", "Yes"),
    c("Industry dummies", "Yes", "Yes","Yes", "Yes"),
    c("Control variables", "Yes", "Yes","Yes", "Yes"),
    c("Cluster", "Sic2", "Sic2", "Sic2", "Sic2")),
  omit.stat = c("rsq", "ser"),
  p.auto = TRUE)

```
